Multi-Robot Probabilistic Mapping and Exploration

### 2018-06-24 Dissertation/Thesis/tex/ae2D.tex
edited up through 3.1

\begin{prop}
\label{prop:ExpectedH}
For candidate ray $z_c$, the expected entropy is
\begin{align}
\label{eqn:DiscExpEntropyRay}
&\text{E}[H(P(m|x_c,z_{c}))]=\sum_{k=1}^{n_{r}+1}\bigg\{H(P(m|x_c,z_{c,k}))P(z_{c,k}|x_c)\bigg\},
\end{align}
where $z_{c,k}$ refers to the distance from $x_c$ to the $k$-th grid cell along the measurement ray. The first term of the summation of \refeqn{DiscExpEntropyRay}, namely $H(P(m|x_c,z_{c,k}))$, is obtained with entropy definitions \refeqn{ShannonsEntropyCell}, \refeqn{ShannonsEntropyMap} and the inverse sensor model \refeqn{RayISMAnswer}--\refeqn{Unnormalized}. The second term is derived from \refeqn{allEta} with
\begin{align}
\label{eqn:ProbMeas}
P(z_{c,k}|x_c)&=\frac{p(z_{c,k}|x_c)}{\sum_{i=1}^{n_{r}+1}p(z_{c,i}|x_c)}=\frac{\eta_{c,k}^{-1}}{\sum_{i=1}^{n_{r}+1}\eta_{c,i}^{-1}},
\end{align}
where $\eta_{c,k}$ refers to the normalizer based on the measurement $z_{c,k}$.
The expected negative entropy change for candidate pose $X_c$ is equivalently the expected information gain,
\begin{align}
\label{eqn:expectedInfoGainRay}
\mathcal I(X_c)&=H(P(m))-\text{E}\left[H(P(m|X_c,Z_c))\right].
\end{align}
\end{prop}
\begin{proof}% TODO: add ref?
See Appendix B.
\end{proof}

@@

% SIMPAR figure on entropy/computation time relationship

>>>>

\begin{prop}
\label{prop:ExpectedH}
For candidate ray $z_c$, the expected entropy is
\begin{align}
\label{eqn:DiscExpEntropyRay}
&\text{E}[H(P(m|x_c,z_{c}))]=\sum_{k=1}^{n_{r}+1}\bigg\{H(P(m|x_c,z_{c,k}))P(z_{c,k}|x_c)\bigg\},
\end{align}
where $z_{c,k}$ refers to the distance from $x_c$ to the $k$-th grid cell along the measurement ray. The first term of the summation of \refeqn{DiscExpEntropyRay}, namely $H(P(m|x_c,z_{c,k}))$, is obtained with entropy definitions \refeqn{ShannonsEntropyCell}, \refeqn{ShannonsEntropyMap} and the inverse sensor model \refeqn{RayISMAnswer}--\refeqn{Unnormalized}. The second term is derived from \refeqn{allEta} with
\begin{align}
\label{eqn:ProbMeas}
P(z_{c,k}|x_c)&=\frac{p(z_{c,k}|x_c)}{\sum_{i=1}^{n_{r}+1}p(z_{c,i}|x_c)}=\frac{\eta_{c,k}^{-1}}{\sum_{i=1}^{n_{r}+1}\eta_{c,i}^{-1}},
\end{align}
where $\eta_{c,k}$ refers to the normalizer based on the measurement $z_{c,k}$.
The expected negative entropy change for candidate pose $X_c$ is equivalently the expected information gain from ray $z_c$,
\begin{align}
\label{eqn:expectedInfoGainRay}
\mathcal I(X_c,z_c)&=H(P(m))-\text{E}\left[H(P(m|X_c,z_c))\right].
\end{align}
\end{prop}
\begin{proof}% TODO: add ref?
See Appendix B.
\end{proof}

@@

\paragraph{Numerical Justification for the Approximation}

The purpose of this numerical example is to provide evidence that the approximations are reasonable and increase the algorithm speed substantially.
Since a measurement ray produces a depth measurement in a single direction, we only consider a 1D map where the grid cells have spacing $\alpha=0.2$ m, and the properties of the range sensor are based on the Microsoft Kinect~\cite{PirRutBisSch11,KhoElb12} with maximum reading depth $z_\text{max}=4$ m ($20$ grid cells inside the sensor FOV). The goal is to compare the expected entropy $\text{E}[H(P(m|x_c,z_{c}))]$ from \refeqn{DiscExpEntropyRay} and with an approximation $\text{E}[H_\text{approx}(P(m|x_c,z_{c}))]$, which only considers $\hat n$ grid cells with highest detection probability \refeqn{ProbOfFirstCell}.

We consider $100$ probabilistic maps to obtain Monte Carlo results to evaluate the approximate entropy. In every Monte Carlo trial, each grid cell has an $80\%$ chance of being free and a $20\%$ chance of receiving an a priori probability uniformly distributed between $0$ and $1$. 
Several metrics serve to evaluate $\text{E}[H(P(m|x_c,z_{c}))]$ with $\text{E}[H_\text{approx}(P(m|x_c,z_{c}))]$. The median expected entropy change is $\text{E}[H(P(m|x_c,z_{c}))]-H(P(m|X_{1:t},Z_{1:t}))=-0.83792$. The error for the $100$ Monte Carlo cases is defined simply as
\begin{align}
e_{H}&=\frac1{100}\sum_{i=1}^{100}\text{abs}\bigg(\text{E}[H(P(m|x_c,z_{c}))]-\text{E}[H_\text{approx}(P(m|x_c,z_{c}))]\bigg).
\end{align}
The Monte Carlo trials are repeated for $\hat n=\braces{1,2,\ldots,10}$ and the results are plotted in Figure \ref{fig:ApproxJust}.
This example shows a typical case when the summation limits generated from \refeqn{ProbOfFirstCell} have only small effects on \refeqn{DiscExpEntropyRay}, while providing very large improvements in reducing computation.

\begin{figure}
	\centering
    	\begin{subfigure}[b]{0.45\textwidth}
        		\includegraphics[width=\textwidth]{JustifyApprox_eH.pdf}
        		\caption{Entropy Error}
        		\label{fig:H_err}
    	\end{subfigure}
	\begin{subfigure}[b]{0.45\textwidth}
        		\includegraphics[width=\textwidth]{JustifyApprox_t.pdf}
        		\caption{Computation Ratio}
        		\label{fig:H_comp_ratio}
    	\end{subfigure}
\caption{The entropy error is decreased at the cost of increasing computation time in this Monte Carlo 1D measurement ray expected entropy case.}
\label{fig:ApproxJust}
\end{figure}
